Individual heterogeneity in the functional network topography of the medial prefrontal cortex

### 2019-05-02 Manuscript.Rmd
more discussion work

However, the interpretation of overlap in group-level data depends on the degree to which functional organization is heterogeneous across individuals. Recent studies have shown that heteromodal brain regions have considerable variability in functional connectivity across individuals [@Muller2013a], individual-specific functional topography can be occluded in aggregative estimations [@Braga2017; @Gordon2017; @Michalka2015; @Tobyne2018], and overlap in functional activation can vanish with increases in spatial precision [@Woo2014]. These findings suggest that group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains.

So far, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive. Therefore, affirming the extent of overlap among psychological processes in this area first requires: 1) a method to reliably and precisely capture its functional topography in isolated individuals; and 2) quantifying the degree of heterogeneity of its intrinsic functional organization in a large group of individuals.

Here we address these challenges by using spectral partitioning, a graph-theoretic clustering algorithm, to reliably subdivide canonical DN and limibic networks [@Yeo2011] on the medial cortex into DN and non-DN in 100 individuals from the Human Connectome Project. Restricting our analyses to this general mPFC/PCC search space makes it appropriate to use a technique that identifies a vertex-wise, binary partitioning. This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use coarser-grained parcels as the units of analysis. SP has advantages (deterministic, simple diagnostics). Comparisons with modularity maximization suggested the binary partitioning was appropriate.

Our results show that the intrinsic functional topography of mPFC and PCC can be reliably partitioned into at least two idiosyncratically arranged networks that can be obscured when averaged across subjects. These sub-networks were stable over time and across test-retest days using moderate amounts of fMRI data (up to 30 min per day), and resembled an organizational scheme recently observed in a handful of subjects [@Braga2017]. We also show that spectral partitioning is capable of identifying these sub-networks in isolated individuals better than more direct seed-based functional connectivity approaches.

>>>>

However, the interpretation of overlap in group-level data depends on the degree to which functional organization is heterogeneous across individuals. Recent studies have shown that heteromodal brain regions have considerable variability in functional connectivity across individuals [@Muller2013a], individual-specific functional topography can be occluded in aggregative estimations [@Braga2017; @Gordon2017; @Michalka2015; @Tobyne2018], and overlap in functional activation can vanish with increases in spatial precision [@Woo2014]. These findings suggest that group-level and meta-analysis-level overlap does not necessarily imply overlap in individual brains. However, our understanding of the individual-level heterogeneity in the functional topography of mPFC has been mostly descriptive so far. Therefore, affirming the extent of overlap among psychological processes in this area first requires: 1) a method to reliably and precisely capture its functional topography in isolated individuals; and 2) quantifying the degree of heterogeneity of its intrinsic functional organization in a large group of individuals.

Here we address these challenges by using spectral partitioning, a graph-theoretic clustering algorithm, to reliably subdivide brain regions that show overlap of DN and valuation effects into DN and non-DN in 100 individuals. Restricting our analyses to this general mPFC/PCC search space made it appropriate to use a technique that identified a vertex-wise, binary partitioning. This contrasts with whole-brain network analyses, which need to allow for multiple sub-networks and which often use coarser-grained parcels as the units of analysis. Unlike some popular clustering algorithms, SP has the advantage of determinisitcally partitioning networks. Comparisons with modularity maximization suggested the binary partitioning was appropriate.

The community structure identified by SP was idiosyncratic across individuals, and stable across test/re-test evaluations within-individuals. We also show that spectral partitioning is capable of identifying these sub-networks in isolated individuals better than more direct seed-based functional connectivity approaches.
